---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# micronutrients

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/WorldHealthOrganization/CRANMicronutrientsSurveyAnalyser/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/WorldHealthOrganization/CRANMicronutrientsSurveyAnalyser/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`micronutrients` is currently an early prototype to compute micronutrient indicators from survey data.
It is based on the code from the [Micronutrient Survey Analyzer tool](https://github.com/WorldHealthOrganization/micronutrients-survey-analyzer-dev/tree/dev).

## Installation

You can install the development version of micronutrients from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("WorldHealthOrganization/CRANMicronutrientsSurveyAnalyser")
```

## API

There are three functions exported at the moment:

* `individual_classification` to compute row level indicators
* `compute_long_format_prevalence` to compute detailed prevalence estimates and other summary statistics
* `compute_short_format_prevalence` to compute less-detailed prevalence estimates and other summary statistics

## Example

To compute row-level classifiction you can do the following:

```{r, eval=FALSE}
dataset <- read.csv("some_data_set")
result <- individual_classification(
  indicators = list(
    iodine_indicator,
    ferritin_indicator(ferritin_adjustment_cutoff),
    ferritin_indicator(no_adjustment),
    anaemia_indicator,
    ida_indicator(no_adjustment)
  ),
  age = dataset$age_years,
  sex = dataset$sex,
  pregnancy_status = dataset$pregnancy_status,
  lactating_status = dataset$lactating_status,
  ferritin = dataset$ferritin_measurement,
  iodine = dataset$iodine,
  CRP = dataset$crp_measurement,
  AGP = dataset$agp_measurement,
  haemoglobin = dataset$haemoglobin_measurement,
  is_smoker = dataset$is_smoker,
  altitude = dataset$altitude,
  smokes_cigarettes_per_day = dataset$smokes_cigarettes_per_day,
  pregnancyweeks = dataset$pregnancyweeks,
  pregnancymonths = dataset$pregnancymonths
)
```

Prevalence functions accept the same arguments and compute a summary table.

```{r, eval=FALSE}
result <- compute_short_format_prevalence(
  indicators = list(
    iodine_indicator,
    ferritin_indicator(ferritin_adjustment_cutoff),
    ferritin_indicator(no_adjustment),
    anaemia_indicator,
    ida_indicator(no_adjustment)
  ),
  age = testdata$age_years,
  sex = testdata$sex,
  pregnancy_status = testdata$pregnancy_status,
  lactating_status = testdata$lactating_status,
  ferritin = testdata$ferritin_measurement,
  iodine = testdata$iodine,
  CRP = testdata$crp_measurement,
  AGP = testdata$agp_measurement,
  haemoglobin = testdata$haemoglobin_measurement,
  is_smoker = testdata$is_smoker,
  altitude = testdata$altitude,
  smokes_cigarettes_per_day = testdata$smokes_cigarettes_per_day,
  pregnancyweeks = testdata$pregnancyweeks,
  pregnancymonths = testdata$pregnancymonths
)
```

## Test coverage

```{r}
covr::package_coverage()
```
